Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex
pass on section 4

@@

Teste cases embedded in issue trackers are an important source of data
as they may have already shown usefulness to reveal problems in some
engine. For example, a developer may have found a corner case that a
given engine did not handle properly. Therefore, it is possible that
other engine do not handle those cases. We thought that we should not
ignore issue trackers for that reason. By manually analyzing a sample
of issues, we observed that developers either 1) add test cases as
attachments of an issue or 2) embed the test cases within the textual
description of an issue. The test cases in attachments are longer
compared to the test cases embedded in issue descriptions whereas the
latter are more common. Consequently, we thought we should handle both
cases.

@@

>>>>

\lbrack{}Dedup\rbrack{}~\Fix{Explain what we did to avoid
  dups. Consider moving to the the sentence ``Finally, note that the number of tests in V8''}

@@

Test cases embedded in issue trackers are an important source of data
as they may have already shown useful to reveal problems in some
engine. For example, a developer may have found a corner case that a
given engine did not handle properly. Therefore, it is possible that
some other engine does not handle that case as well. For that reasons,
we thought that we should not ignore issue trackers. By manually
analyzing a sample of issues, we observed that developers either 1)
add test cases as attachments of an issue or 2) embed the test cases
within the textual description of an issue. The test cases in
attachments are longer compared to the test cases embedded in issue
descriptions whereas the latter are more common. Consequently, we
thought we should handle both cases.

@@

\subsection{Characterization of Test Suites}

\Fix{...add and discuss histograms}
